A Continuous Occlusion Model for Road Scene Understanding

### 2016-06-22 poster/poster.tex
Changes

    \end{column}
    \begin{column}{\sepwid}\end{column}			% empty spacer column
    \begin{column}{2.0\onecolwid}
      \begin{block}{Experiments}
        \begin{columns}[t]
          \column{1.000\onecolwid}
          \begin{table}
            \begin{tabular}{lrrrr}
              \toprule
              Point tracks & Ours & BBox & BM & RAS\\
              \midrule
              Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
              Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
              Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
              All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
              \bottomrule
            \end{tabular}
            \caption{\small Mean association errors on different sets of input point tracks over all sequences. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
          \end{table}
          \column{1.000\onecolwid}
          \begin{table}
            \begin{tabular}{lrr}
              \toprule
              Method & t & dim \\
              \midrule
              Point cloud fitting
              & 6.87 & 4.02\\
              Initialization by~\cite{Song_Chandraker_2014}
              & 5.61 & 3.23\\
              $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
              & 3.95  & 1.72\\        
              $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
              & 4.81  & 2.16\\        
              $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
              & 4.05  & {\bf 1.59}\\        
              $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
              & {\bf 3.24}  & 2.16\\
              \bottomrule
            \end{tabular}
            \caption{\small Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
          \end{table}
        \end{columns}

@@

	  \textbf{3D Object Localization:}
		\begin{figure}
			\newcommand{\imagewidth}{18cm}
		      \hspace{-0.8cm}
		    \input{Source/scenelayoutoverlayCity0961} \\
		      \hspace{-0.8cm}
		    \input{Source/graphical_model_multiple}        
        \end{figure}	
        \begin{multline*}
          -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\textbf{d}^i(t)\} )} = \\
          -\tilde{Z} 
          + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
          +  
          \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
          \left(
            \lambda_{\text{detect}}\EnergyBBox
            + \lambda_{\text{dyn}}\EnergyDyn    
            + \lambda_{\text{size}}\EnergySize
          \right)
          \enspace
        \end{multline*}        
        \begin{align}
		  \pEnergy{track} = \sum_{i=1}^{N} \sum_{j = 1}^{M} \int_0^\infty a^{ij}(\lambda) E^{ij}_{\textit{reproj}}(\lambda) d\lambda
		\end{align}        
        \begin{equation}
			S(\textbf{d}^i(t)) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right)
		\end{equation}		
		\begin{align}
		  \Theta_{i}(\bu, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \bu)
		\end{align}		
		\begin{align}
		  \Energy{detect} = \frac{1}{S'(\textbf{d}^i(t))}
		\end{align}

>>>>

    \end{column}
    \begin{column}{\sepwid}\end{column}			% empty spacer column
    \begin{column}{2.0\onecolwid}
      \begin{block}{Experiments}
        \begin{columns}[t]
          \column{1.000\onecolwid}
          \begin{table}
            \begin{tabular}{lrrrr}
              \toprule
              Point tracks & Ours & BBox & BM & RAS\\
              \midrule
              Dynamic \& occluded         & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
              Occluded		              & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
              Dynamic		              & \textbf{6.6} & 11.4 & 15.3 & 17.7 \\
              All		                  & \textbf{8.6} & 12.6 & 21.9 & 21.5 \\
              \bottomrule
            \end{tabular}
            \caption{\small Mean association errors on different sets of input point tracks over all sequences. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
          \end{table}
          \column{1.000\onecolwid}
          \begin{table}
            \begin{tabular}{lrr}
              \toprule
              Method & t & dim \\
              \midrule
              Point cloud fitting
              & 6.87 & 4.02\\
              Initialization by~\cite{Song_Chandraker_2014}
              & 5.61 & 3.23\\
              $\EnergyTrackNoOcc + \Energy{detectNoOcc} +\EnergySize+\EnergyDyn$ 
              & 3.95  & 1.72\\        
              $\EnergyTrackNoOcc + \Energy{detect} +\EnergySize+\EnergyDyn$        
              & 4.81  & 2.16\\        
              $\EnergyTrack + \Energy{detectNoOcc} +\EnergySize+\EnergyDyn$      
              & 4.05  & {\bf 1.59}\\        
              $\EnergyTrack + \Energy{detectNoOcc} +\EnergySize+\EnergyDyn$             
              & {\bf 3.24}  & 2.16\\
              \bottomrule
            \end{tabular}
            \caption{\small Localization experiment results with different combinations of energies. We report translation error (t) and dimension error (dim) in meters per car. Yaw angles for static objects are not optimized by our model. These experiments use the set of occluded tracks to demonstrate the effect of our modeling.}
          \end{table}
        \end{columns}

@@

	  \textbf{3D Object Localization:}
		\begin{figure}
			\newcommand{\imagewidth}{18cm}
		      \hspace{-0.8cm}
		    \input{Source/scenelayoutoverlayCity0961} \\
		      \hspace{-0.8cm}
		    \input{Source/graphical_model_multiple}        
        \end{figure}	
        \begin{multline*}
          -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\textbf{d}^i(t)\} )} = \\
          -\tilde{Z} 
          + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
          +  
          \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
          \left(
            \lambda_{\text{detect}}\Energy{detect}
            + \lambda_{\text{dyn}}\EnergyDyn    
            + \lambda_{\text{size}}\EnergySize
          \right)
          \enspace
        \end{multline*}        
        \begin{align}
		  \pEnergy{track} = \sum_{i=1}^{N} \sum_{j = 1}^{M} \int_0^\infty a^{ij}(\lambda) E^{ij}_{\textit{reproj}}(\lambda) d\lambda
		\end{align}        
        \begin{equation}
			S(\textbf{d}^i(t)) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right)
		\end{equation}		
		\begin{align}
		  \Theta_{i}(\bu, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \bu)
		\end{align}		
		\begin{align}
		  \Energy{detect} = \frac{1}{S'(\textbf{d}^i(t))}
		\end{align}
